---
title: "ToyPackageMarkdown"
author: "Laura Falk"
date: "2023-04-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Create repo. don't use symbols or spaces

Load req packages
```{r}
library(devtools)
library(here)
```

```{r}
#create_package(here())
```

This only works in the console?
```{r}
#use_readme_md()
```
load_all() loads the functions in a package theoretically

document() writes doc for package

?greet now populates the help

install() installs the packages in the r folder. look for green check marks.

```{r}
library(cli)
# color stuffs
```

check() checks the package. ex: dependencies  

use_package("cli") in console will add dependencies. look at DESCRIPTION under IMPORTS

there is still a common error. What is it?!

must refer to outside packages within functions (cli::) unless base R EVERYTHING needs the reference

```{r}
mydata <- iris
```

use_data(mydata) creates a data folder and notes dependencies
look at 'https://r-pkgs.org/data.html'
create a new r script called data.R. copy format from website.
save it in the R folder.

document() updates files?

use_testthat() edits descriptions and creates tests folder

use_test("greet") creates new file in tests>testthat

test_that("greet works without a name", {
  expect_message(greet(), "Hello User!")
})


change cat() to

use_github_action_check_release() creates a .github folder. 
this fails because reasons

use_pkgdown()
use_pkgdown_github_pages()
this makes a github page for the package!

use_code_of_conduct()

usE_license() ?? possibly?

https://r-pkgs.org/data.html#sec-documenting-data

